Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-03-10 hotstorage13/abs.tex

\begin{abstract}
%Virtualization has became the engine behind many cloud computing platforms.
In a virtualized cloud cluster, frequent  snapshot backup of virtual disks improves
hosting  reliability; however, it  takes significant 
memory resource to perform data duplication in order to remove
excessive redundancy among snapshots.
This paper presents a low-cost deduplication solution scalable for a large number 
of virtual machines.  The key idea is to separate duplicate detection from 
the actual storage backup instead of using inline deduplication, and partition
global index and  detection requests among machines using  fingerprint values.
Then each machine conducts duplicate detection partition by partition independently with a minimal memory usage.
%in parallel among all machines and  each machine full duplication detection is 
Another optimization is to allocate and control
buffer space for exchanging  detection requests and duplicate summary among machines.
%The memory requirement and disk usage for the proposed solution is very small while the overall thoughput
%and backup process timing is not compromised. 
Our evaluation shows that  the proposed multi-phase scheme 
uses a very small amount of system resources while delivering a satisfactory backup throughput.
%in a large cloud setting.
%which only reqiires a very small amount of memory and CPU resource.  
%Experimental results  show the proposed scheme  can achieve high deduplication ratio while using
%a  small  amount of cloud resources.

>>>>

\begin{abstract}
%Virtualization has became the engine behind many cloud computing platforms.
In a virtualized cloud cluster, frequent  snapshot backup of virtual disks improves
hosting  reliability; however, it  takes significant 
memory resource to perform data duplication in order to remove
excessive redundancy among snapshots.
This paper presents a low-cost deduplication solution scalable for a large number 
of virtual machines.  The key idea is to separate duplicate detection from 
the actual storage backup instead of using inline deduplication, and partition
global index and  detection requests among machines using  fingerprint values.
Then each machine conducts duplicate detection partition by partition independently with a minimal memory usage.
%in parallel among all machines and  each machine full duplication detection is 
Another optimization is to allocate and control
buffer space for exchanging  detection requests and duplicate summary among machines.
%The memory requirement and disk usage for the proposed solution is very small while the overall thoughput
%and backup process timing is not compromised. 
Our evaluation shows that  the proposed multi-stage scheme 
uses a very small amount of system resources while delivering a satisfactory backup throughput.
%in a large cloud setting.
%which only reqiires a very small amount of memory and CPU resource.  
%Experimental results  show the proposed scheme  can achieve high deduplication ratio while using
%a  small  amount of cloud resources.
